\documentclass{sigcomm-alternate}
\pdfpagewidth=8.5in
\pdfpageheight=11in

% added by Vaibhav
%----------------------------------------------------------------------
\usepackage{cite}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage[T1]{fontenc}
\usepackage[nolist]{acronym}
\usepackage{url}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{listings}
\usepackage[font=footnotesize,caption=false]{subfig}
\usepackage[multiple]{footmisc}
\usepackage{color,soul}
\usepackage{amsfonts}
\usepackage{epigraph}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}

\definecolor{gray}{gray}{0.93}
%----------------------------------------------------------------------

\input{acronyms.tex}
\begin{document}

\title{Dagstuhl Perspectives Workshop on Global Measurements: Practice and
Experience}
\title{Global Measurements: Practice and Experience \\ (Report on Dagstuhl Seminar \#16012)}

\numberofauthors{1}
\author{
\begin{tabular*}{0.9\textwidth}%
{@{\extracolsep{\fill}}ccc}
Vaibhav Bajpai & Arthur W. Berger & Philip Eardley \\
\affaddr{Jacobs University} & \affaddr{Akamai Technologies} & \affaddr{British Telecom R\&D} \\
\affaddr{Bremen, DE} & \affaddr{Cambridge, US} & \affaddr{Ipswich, GB} \\
\email{v.bajpai@jacobs-university.de} & \email{awberger@csail.mit.edu} & \email{philip.eardley@bt.com}
\end{tabular*}\\
\begin{tabular}{c}
\end{tabular}\\
\begin{tabular*}{0.6\textwidth}%
{@{\extracolsep{\fill}}cc}
Jörg Ott & Jürgen Schönwälder \\
\affaddr{TU München} & \affaddr{Jacobs University} \\
\affaddr{München, DE} & \affaddr{Bremen, DE} \\
\email{ott@in.tum.de} & \email{j.schoenwaelder@jacobs-university.de}
\end{tabular*}\\
\begin{tabular}{c}
\end{tabular}\\
\begin{tabular}{c}
{\normalsize This article is an editorial note submitted to CCR. It has NOT
been peer reviewed.}\\
{\normalsize The authors take full responsibility for this article's
technical content. Comments can be posted through CCR Online.}
\end{tabular}
}

\maketitle

\begin{abstract}

This article summarises a 2.5 day long Dagstuhl seminar on Global
Measurements: Practice and Experience held in January 2016.  This seminar was
a followup of the seminar on Global Measurement Frameworks held in 2013, which
focused on the development of global Internet measurement platforms and
associated metrics.  The second seminar aimed at discussing the practical
experience gained with building these global Internet measurement platforms.
It brought together people who are actively involved in the design and
maintenance of global Internet measurement platforms and who do research on
the data delivered by such platforms. Researchers in this seminar have used
data derived from global Internet measurement platforms in order to manage
networks or services or as input for regulatory decisions. The entire set of
presentations delivered during the seminar is made publicly available at
\cite{dagstuhl-materials}.

\end{abstract}

% referrred: http://www.acm.org/about/class/ccs98-html
%\category{C.2.3}{Computer-Communication Networks}{Network Operations}[Network
%monitoring]

% referred: http://www.acm.org/sigs/publications/sigguide-v2.2sp
%\terms{Measurement, Performance}

\keywords{Internet measurements, Quality of experience, Network management,
Traffic engineering}

% sections
%----------------------------------------------------------------------
\input{sections/introduction}
\input{sections/invited-presentations}
\input{sections/parallel-group-work}
\input{sections/lightning-talks}
\input{sections/conclusion}
\input{sections/acknowledgements}
%----------------------------------------------------------------------

% bibliography
%----------------------------------------------------------------------
\bibliographystyle{abbrv}

\begin{thebibliography}{10}

\bibitem{dagstuhl-materials}
{Dagstuhl Seminar \#16012 – Global Measurements: Practice and Experience:
  Materials}.
\newblock \url{http://materials.dagstuhl.de/index.php?semnr=16012}.
\newblock [Online; accessed 18-January-2016].

\bibitem{flamingo}
{Flamingo - Management of the Future Internet}.
\newblock \url{http://www.fp7-flamingo.eu}.
\newblock [Online; accessed 18-January-2016].

\bibitem{leone}
{Leone - From Global Measurements to Local Management}.
\newblock \url{http://www.leone-project.eu}.
\newblock [Online; accessed 18-January-2016].

\bibitem{mami}
{MAMI - Measurement and Architecture for a Middleboxed Internet}.
\newblock \url{https://mami-project.eu}.
\newblock [Online; accessed 18-January-2016].

\bibitem{mba}
{Measuring Broadband America - Federal Communications Commission}.
\newblock \url{https://www.fcc.gov/general/measuring-broadband-america}.
\newblock [Online; accessed 18-January-2016].

\bibitem{soti}
{State of the Internet - Akamai}.
\newblock \url{https://www.stateoftheinternet.com}.
\newblock [Online; accessed 18-January-2016].

\bibitem{ethics}
{Workshop on Ethics in Networked Systems Research - ACM SIGCOMM 2015}.
\newblock \url{http://conferences.sigcomm.org/sigcomm/2015/netethics.php}.
\newblock [Online; accessed 18-January-2016].

\bibitem{ripencc:ipj:2015}
{RIPE Atlas: A Global Internet Measurement Network}.
\newblock {\em Internet Protocol Journal}, Sept. 2015.

\bibitem{mallman:imc:2007}
M.~Allman and V.~Paxson.
\newblock {Issues and Etiquette Concerning Use of Shared Measurement Data}.
\newblock IMC '07, pages 135--140. ACM, 2007.

\bibitem{anonymous:ccr:2012}
Anonymous.
\newblock {The Collateral Damage of Internet Censorship by DNS Injection}.
\newblock {\em SIGCOMM Comput. Commun. Rev.}, 42(3):21--27, June 2012.

\bibitem{vbajpai:ccr:2015}
V.~Bajpai, S.~J. Eravuchira, and J.~Sch\"{o}nw\"{a}lder.
\newblock {Lessons Learned From Using the RIPE Atlas Platform for Measurement
  Research}.
\newblock {\em SIGCOMM Comput. Commun. Rev.}, 45(3):35--42, July 2015.

\bibitem{vbajpai:comst:2015}
V.~Bajpai and J.~Sch\"onw\"alder.
\newblock {A Survey on Internet Performance Measurement Platforms and Related
  Standardization Efforts}.
\newblock {\em Communications Surveys Tutorials, IEEE}, 17(3):1313--1341,
  thirdquarter 2015.

\bibitem{sburnett:sigcomm:2015}
S.~Burnett and N.~Feamster.
\newblock {Encore: Lightweight Measurement of Web Censorship with Cross-Origin
  Requests}.
\newblock SIGCOMM '15. ACM, 2015.

\bibitem{jcappos:sigcse:2009}
J.~Cappos, I.~Beschastnikh, A.~Krishnamurthy, and T.~Anderson.
\newblock {Seattle: A Platform for Educational Cloud Computing}.
\newblock SIGCSE '09. ACM, 2009.

\bibitem{fchen:sigcomm:2015}
F.~Chen, R.~K. Sitaraman, and M.~Torres.
\newblock {End-User Mapping: Next Generation Request Routing for Content
  Delivery}.
\newblock SIGCOMM '15. ACM, 2015.

\bibitem{kclaffy:ccr:2016}
k.~claffy.
\newblock {The 7th Workshop on Active Internet Measurements (AIMS7) Report}.
\newblock {\em SIGCOMM Comput. Commun. Rev.}, 46(1):50--57, Jan. 2016.

\bibitem{jcohen:dagstuhl:2014}
J.~E. Cohen, S.~Dietrich, A.~Pras, L.~D. Zuck, and H.~Mireille.
\newblock {Ethics in Data Sharing (Dagstuhl Seminar 14052)}.
\newblock {\em Dagstuhl Reports}, 4(1):170--183, 2014.

\bibitem{gdetal:imc:2013}
G.~Detal, B.~Hesmans, O.~Bonaventure, Y.~Vanaubel, and B.~Donnet.
\newblock {Revealing Middlebox Interference with Tracebox}.
\newblock IMC '13. ACM, 2013.

\bibitem{roland:creds:2014}
S.~Dietrich, J.~van~der Ham, A.~Pras, R.~van Rijswijk-Deij, D.~Shou,
  A.~Sperotto, A.~van Wynsberghe, and L.~Zuck.
\newblock {Ethics in Data Sharing: developing a model for best practice}.
\newblock CREDS II, 2014.

\bibitem{mdischinger:imc:2007}
M.~Dischinger, A.~Haeberlen, K.~P. Gummadi, and S.~Saroiu.
\newblock {Characterizing Residential Broadband Networks}.
\newblock IMC '07. ACM, 2007.

\bibitem{menloreport}
D.~Dittrich and E.~Kenneally.
\newblock {The Menlo Report: Ethical Principles Guiding Information and
  Communication Technology Research}.
\newblock Technical report, U.S. Department of Homeland Security, 2012.

\bibitem{bstiller:aims:2015}
D.~D{\"{o}}nni, G.~S. Machado, C.~Tsiaras, and B.~Stiller.
\newblock {Schengen Routing: {A} Compliance Analysis}.
\newblock In {\em {AIMS} 2015, Ghent, Belgium, June 22-25, 2015.}, 2015.

\bibitem{cdovrolis:ccr:2010}
C.~Dovrolis, K.~Gummadi, A.~Kuzmanovic, and S.~D. Meinrath.
\newblock {Measurement Lab: Overview and an Invitation to the Research
  Community}.
\newblock {\em SIGCOMM Comput. Commun. Rev.}, 40(3):53--56, June 2010.

\bibitem{peardley:dagstuhl:2013}
P.~Eardley, M.~Mellia, J.~Ott, J.~Sch{\"o}nw{\"a}lder, and H.~Schulzrinne.
\newblock {Global Measurement Framework (Dagstuhl Seminar 13472)}.
\newblock {\em Dagstuhl Reports}, 2014.

\bibitem{rfc7594}
P.~Eardley, A.~Morton, M.~Bagnulo, T.~Burbridge, P.~Aitken, and A.~Akhter.
\newblock {A Framework for Large-Scale Measurement of Broadband Performance
  (LMAP)}.
\newblock RFC 7594 (Informational), Sept. 2015.

\bibitem{gcarle:imc:2015}
P.~Emmerich, S.~Gallenm\"{u}ller, D.~Raumer, F.~Wohlfart, and G.~Carle.
\newblock {MoonGen: A Scriptable High-Speed Packet Generator}.
\newblock IMC '15. ACM, 2015.

\bibitem{draft-tsvwg-quic-protocol}
R.~Hamilton, J.~Iyengar, I.~Swett, and A.~Wilk.
\newblock {QUIC: A UDP-Based Secure and Reliable Transport for HTTP/2}.
\newblock Internet-Draft draft-tsvwg-quic-protocol-02, Internet Engineering
  Task Force, Jan. 2016.

\bibitem{mhonda:imc:2011}
M.~Honda, Y.~Nishida, C.~Raiciu, A.~Greenhalgh, M.~Handley, and H.~Tokuda.
\newblock {Is It Still Possible to Extend TCP?}
\newblock IMC '11. ACM, 2011.

\bibitem{pgill:comcom:2011}
B.~Krishnamurthy, W.~Willinger, P.~Gill, and M.~Arlitt.
\newblock {A Socratic method for validation of measurement-based networking
  research}.
\newblock {\em Computer Communications}, 34(1):43 -- 53, 2011.

\bibitem{skrishnan:imc:2012}
S.~S. Krishnan and R.~K. Sitaraman.
\newblock {Video Stream Quality Impacts Viewer Behavior: Inferring Causality
  Using Quasi-experimental Designs}.
\newblock IMC '12, 2012.

\vfill\eject

\bibitem{mluckie:imc:2010}
M.~Luckie.
\newblock {Scamper: A Scalable and Extensible Packet Prober for Active
  Measurement of the Internet}.
\newblock IMC '10. ACM, 2010.

\bibitem{mfiedler:commantel:2013}
T.~N. Minhas and M.~Fiedler.
\newblock {Quality of experience hourglass model}.
\newblock In {\em ComManTel 2013}, Jan 2013.

\bibitem{draft-ietf-ippm-active-passive}
A.~Morton.
\newblock {Active and Passive Metrics and Methods (and everything in-between,
  or Hybrid)}.
\newblock Internet-Draft draft-ietf-ippm-active-passive-06, Internet
  Engineering Task Force, Jan. 2016.

\bibitem{hnam:infocom:2016}
H.~Nam, K.-H. Kim, and H.~Schulzrinne.
\newblock {QoE Matters More Than QoS: Why People Stop Watching Cat Videos}.
\newblock In {\em INFOCOM, 2016 (to appear)}, April 2016.

\bibitem{apathak:pam:2010}
A.~Pathak, Y.~A. Wang, C.~Huang, A.~Greenberg, Y.~C. Hu, R.~Kern, J.~Li, and
  K.~W. Ross.
\newblock {Measuring and Evaluating TCP Splitting for Cloud Services}.
\newblock PAM'10, pages 41--50. Springer-Verlag, 2010.

\bibitem{vpaxson:imc:2004}
V.~Paxson.
\newblock {Strategies for Sound Internet Measurement}.
\newblock IMC '04, pages 263--271. ACM, 2004.

\bibitem{ssundaresan:arxiv:2015}
A.~Razaghpanah, N.~Vallina{-}Rodriguez, S.~Sundaresan, C.~Kreibich, P.~Gill,
  M.~Allman, and V.~Paxson.
\newblock {Haystack: In Situ Mobile Traffic Analysis in User Space}.
\newblock {\em CoRR}, abs/1510.01419, 2015.

\bibitem{rteixeira:pam:2012}
A.~Reggani, F.~Schneider, and R.~Teixeira.
\newblock {An End-Host View on Local Traffic at Home and Work}.
\newblock {PAM} '12, pages 21--31, 2012.

\bibitem{rbush:jsac:2011}
M.~Roughan, W.~Willinger, O.~Maennel, D.~Perouli, and R.~Bush.
\newblock {10 Lessons from 10 Years of Measuring and Modeling the Internet's
  Autonomous Systems}.
\newblock {\em JSAC}, 29(9):1810--1821, October 2011.

\bibitem{gcarle:tma:2015}
J.~Schlamp, R.~Holz, O.~Gasser, A.~Korsten, Q.~Jacquemart, G.~Carle, and E.~W.
  Biersack.
\newblock {Investigating the Nature of Routing Anomalies: Closing in on
  Subprefix Hijacking Attacks}.
\newblock {TMA} '15.

\bibitem{rsitaraman:wiley:2014}
R.~K. Sitaraman, M.~Kasbekar, W.~Lichtenstein, and M.~Jain.
\newblock {\em {Overlay Networks: An Akamai Perspective}}, pages 305--328.
\newblock John Wiley \& Sons, Inc., 2014.

\bibitem{ssonntag:wiopt:2013}
S.~Sonntag, J.~Manner, and L.~Schulte.
\newblock {Netradar - Measuring the wireless world}.
\newblock WiOpt '13, May 2013.

\bibitem{ssundaresan:usenix:2014}
S.~Sundaresan, S.~Burnett, N.~Feamster, and W.~De~Donato.
\newblock {BISmark: A Testbed for Deploying Measurements and Applications in
  Broadband Access Networks}.
\newblock USENIX ATC'14, pages 383--394, 2014.

\bibitem{ssundaresan:pam:2015}
S.~Sundaresan, N.~Feamster, and R.~Teixeira.
\newblock {Measuring the Performance of User Traffic in Home Wireless
  Networks}.
\newblock {PAM} '15, pages 305--317, 2015.

\bibitem{btrammell:commag:2014}
B.~Trammell, P.~Casas, D.~Rossi, A.~Bar, Z.~Houidi, I.~Leontiadis, T.~Szemethy,
  and M.~Mellia.
\newblock {mPlane: an Intelligent Measurement Plane for the Internet}.
\newblock {\em IEEE Communications Magazine}, 52(5):148--156, May 2014.

\bibitem{roland:tnc:2015}
R.~van Rijswijk-Deij.
\newblock {Ethics in Data Sharing: a best practice for NRENs}.
\newblock TNC '15. G\'{E}ANT, 2015.

\bibitem{roland:sigcomm:2015}
R.~van Rijswijk-Deij, M.~Jonker, A.~Sperotto, and A.~Pras.
\newblock {The Internet of Names: A DNS Big Dataset}.
\newblock SIGCOMM '15, pages 91--92. ACM, 2015.

\bibitem{twhite:oreilly:2015}
T.~White.
\newblock {\em {Hadoop - The Definitive Guide: Storage and Analysis at Internet
  Scale {(4.} ed., revised {\&} updated)}}.
\newblock O'Reilly, 2015.

\end{thebibliography}

%----------------------------------------------------------------------

\end{document}
